# Wine Price Prediction Using Linear Regression

## Synopsis
The data gives the wine prices and other factors. A linear regression analysis is used to predict wine's price. 
## Download Data

```{r, cache=T}
wine = read.csv('wine.csv')
wineTest = read.csv('wine_test.csv')
names(wine)
```
For each elements, a scatter plot is made to show the relation between price and the factor. Both AGST and HarvestRain show the highest influences over the French wine price. 
```{r}
par(mfrow = c(1, 2))
model1 = lm(Price~AGST, data=wine)
with(wine, plot(AGST, Price))
abline(model1)

model1 = lm(Price~HarvestRain, data=wine)
with(wine, plot(HarvestRain, Price))
abline(model1)
```
## Linear Regression

Now consider AGST and HarvestRain both as variables to predict the wine price using linear regression. 

```{r}
model2 = lm(Price~AGST+HarvestRain, data=wine)
predictTest = predict(model2, newdata=wineTest)
```
Model2 with AGST and HarvestRain is better than Model1 with only AGST, which is shown through the increasing of adjusted R-squared. The perfect model would have adjusted R-squared as 1.0.  
```{r}
summary(model1)
summary(model2)
```

```{r}
#===============Plotting Results==============
# cut the wine price into 4 bins just to show the relationship of Price vs AGST and HarvestRain.
wine$PriceRange = cut(wine$Price, 4)
with(wine, plot(AGST, HarvestRain, pch=unclass(wine$PriceRange)))
legend('topright', pch=unique(unclass(wine$PriceRange)), legend = unique(wine$PriceRange))
# pick up three binning points for prices. The goal is to draw the division lines of price range using linear regression results
q = c(6.78, 7.35, 7.92)
theta= coef(model2)
abline(coef = c((theta[1]-q[1])/(-1.0*theta[3]), theta[2]/(-1*theta[3])), col='blue', lwd= 2.0)
abline(coef = c((theta[1]-q[2])/(-1.0*theta[3]), theta[2]/(-1*theta[3])), col='red', lwd= 2.0)
abline(coef = c((theta[1]-q[3])/(-1.0*theta[3]), theta[2]/(-1*theta[3])), col='purple', lwd= 2.0)
legend('bottomleft', lwd = 2.0, 
lty = 1.0, col = c('blue', 'red', 'purple'), legend = q)
title('Linear Regression Visualization')
```
